---
title: "Vulgar language on the web across World Englishes - Part 2: data processing"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
  tufte::tufte_handout:
    latex_engine: xelatex
bibliography: bibliography.bib
link-citations: yes
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Intro

This document shows an analysis that was performed with the aim of finding differences in swearing across geographically distinct varieties of English around the world based on the GloWbE corpus. 

install packages

```{r install, eval = F, message=F, warning=F}
# install packages
install.packages("tidyverse")
install.packages("quanteda")
install.packages("here")
install.packages("udpipe")
install.packages("future")
install.packages("furrr")
install.packages("stringi")
install.packages("parallel")
install.packages("usethis")
install.packages("data.table")
devtools::install_github("jimjam-slam/ggflags")
install.packages("ggflags")
```

load packages and set options

```{r act, message=FALSE, warning=FALSE}
# load packages
library(data.table)
library(tidyverse)
library(quanteda)
library(here)
library(stringi)
library(parallel)
library(usethis)
library(data.table)
library(ggflags)
```

# data preparation

# loading data

raw

```{r}
# paths to results
cdfs <- list.files(here::here("test"), pattern = "dfc.rda", full.names = T)
# load tables
lapply(cdfs, function(x) {
  x <- readRDS(x)
  }) -> lcdfs 
# combine into a single df 
data.table::rbindlist(lcdfs)   %>%
  # remove NAs
  dplyr::filter(txt != "") -> cdf
# clean
cdf  %>% 
  dplyr::mutate(sfl = stringr::str_remove_all(sfl, ".txt.*")) %>%
  # rename columns
  dplyr::rename(corpus = crp,
                file = sfl,
                subfile = fl,
                rawtext = txt,
                cleantext = ctxt) -> df
# inspect clean dataframe
head(df)
```

create summary table

```{r}
df  %>%
  dplyr::ungroup() %>%
  dplyr::mutate(# count number of words
    words = length(unlist(quanteda::tokenize_fastestword(cleantext))),
    # determine type of data (blog vs general web)
    type = dplyr::case_when(stringr::str_detect(file, "^w_") ~ "General Web",
                            TRUE ~ "Blog")) -> dfw
# save
#base::saveRDS(dfw, file = here::here("test", "glowbe.rda"))
# inspect
head(dfw)
```

extract basic information

```{r}
# info table
dfw %>%
  dplyr::group_by(corpus, file, subfile, type) %>%
  dplyr::summarise(tokens = sum(words))  -> glowbe_table 
# save
#base::saveRDS(glowbe_table, file = here::here("test", "glowbe_table.rda"))
# inspect
head(glowbe_table)
```

save and reload results

```{r eval = F}
dfw <- base::readRDS(file = here::here("test", "glowbe.rda"))
glowbe_table <- base::readRDS(file = here::here("test", "glowbe_table.rda"))
```

# load kwics

```{r}
# paths to results
kwics <- list.files(here::here("test"), pattern = "_kwic_results.rda", full.names = T)
# inspect
kwics
```

process kwics and combine into a single dataframe

```{r}
# load tables
lapply(kwics, function(x) {
  x <- readRDS(x)
  }) -> kwicdfs 
# combine into a single df 
data.table::rbindlist(kwicdfs) -> kwicdf
# inspect
head(kwicdf)
```

## Lemma

annotate lemmas

```{r}
kwicdf_annotated <- kwicdf %>% 
  dplyr::mutate(lemma = dplyr::case_when(pattern ==  "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå]r[s5$§z][e3€ëéê][h]?[o0øöóõ]*[l1£][e3€ëéê]*[s5$§z]*\\b" ~  "arse(hole)",
                                         pattern == "\\b(dumb|stupid|lazy|worthless|useless|brain|dead|jack)*[a@4äáå][s5$§z]{2,}[h]?[o0øöóõ]*[l1|£][e3€ëéê]*[s5$§z]*\\b" ~ "ass(hole)",
    pattern == "\\b[8ß|3][i1!|ïíì]+[a@4äáå]*[t7+†][c¢©(][h](es|ez|ing|ed)*\\b" ~ "bitch",
    pattern == "\\b[8ß|3][a@4äáå][s5$§z][t7+†][a@4äáå]r[d][o]*(s|z)*\\b" ~ "bastard",
    pattern == "\\b[8ß|3][e3€ëéê][a@4äáå]n[e3€ëéê]r(s|z)*\\b" ~ "beaner",
    pattern ==   "\\b[8ß|3][e3€ëéê]ll[e3€ëéê]nd(s|z)*\\b" ~ "bellend",
    pattern ==     "\\b[8ß|3][1!|ïíì]mb[o0øöóõ](s|z)*\\b" ~ "bimbo",
    pattern == "\\bbl[o0øöóõ]{2,}d[iy¥](ed)*\\b" ~ "bloody",
    pattern == "\\b[8ß|3][o0øöóõ]ll[o0øöóõiïíì][xc¢©(k|<{(]+[s5$§z]?\\b" ~ "bollocks",
    pattern == "\\bboner[s]*\\b" ~ "boner", 
    pattern == "\\b[8ß|3][o0øöóõ]n[k|<{(](in|ing)*\\b" ~ "bonk",
    pattern == "\\b[8ß|3][o0øöóõ]{2,}[b8ß|3][ie]*[s5$§z]?\\b" ~ "boobs",
    pattern == "\\b[8ß|3][u|µüúû]gg[e3€ëéê]r(ing|s|z)*\\b" ~ "bugger",
    pattern == "\\b[b8ß|3][u|µüúû]ll[s5$§z]h[1!|ïíì]+[t7+†]*\\b" ~ "bullshit",
    pattern == "\\b[b8ß3][uµüúû][t7+†][t7+†][sz]*(face|head|wit|whipe|hole|h)*[hl]*[sz]*\\b" ~ "butt(hole)",
    pattern == "\\b(god)*damn\\b" ~ "damn",
    pattern == "\\bdarki(es)*\\b" ~ "darkie",
    pattern == "\\b(bull)*d[iy]*ke(s|z)*\\b" ~ "dike",
    pattern == "\\bdildo(s|z)*\\b" ~ "dildo",
    pattern == "\\bdork(s|z)*\\b" ~ "dork",
    pattern == "\\beff(ing|in|ed|d)*[-._+ ]*[(you|up|off)]*\\b" ~ "eff",
    pattern == "\\bfann(y|ies)+\\b" ~ "fanny",
    pattern == "\\bfart(s|z|ing|in|ed)*\\b" ~ "fart",
    pattern == "\\bfrig(g|gin|ging|ged|gs)*\\b" ~ "frig",
    pattern == "\\b(cluster|head|mother|motha|mutha|mada|cock|mom|mum|daddy|father|sister|brother)*[f=ƒ][uµüúû|@a4äáå|e3€ëéê|o0øöóõ|*]*[c¢©(]*[k|<{(][e3€ëéê]*[r]*(head|face|wit|ing|er|a|ed|ers|az)*\\b" ~ "fuck",
    pattern == "\\bf[-._+ ](me|you|it|this|that|the|these|those|him|her|us|them)+\\b" ~ "fuck",
    pattern == "\\b[f=ƒ][c¢©(*k<{(uµüúû*]+\\b" ~ "fuck",
    pattern == "\\bgash\\b" ~ "gash",
    pattern == "\\bg[o]*ok(s|z)*\\b" ~ "gook",
    pattern == "\\bidiot(s|z)*\\b" ~ "idiot",
    pattern == "\\bjacka[s5$§z][s5$§z]\\b" ~ "jackass",
    pattern == "\\bjap[zs]*\\b" ~ "jap",
    
    pattern == "\\bjerk(s|z|in|ing|ed)*\\b" ~ "jerk",
    pattern == "\\bji[s5$§z][s5$§z]+\\b" ~ "jiss",
    pattern == "\\bjug[g]*[s5$§z]*\\b" ~ "jug",
    pattern == "\\b[(dip)]*[s5$§z]h[1!|ïíì]+[t7+†]*(ing|e|in|er|a|ed|ers|az|s|z)*\\b" ~ "shit",
    pattern == "\\bktfo\\b" ~ "online",
    pattern == "\\bstfu\\b" ~ "online",
    pattern == "\\bgtfo\\b" ~ "online",
    pattern == "\\bngaf\\b" ~ "online",
    pattern == "\\bdgaf\\b" ~ "online",
    pattern == "\\bffs\\b" ~ "online",
    pattern == "\\bfml\\b" ~ "online",
    pattern == "\\bomfg\\b" ~ "online",
    pattern == "\\baf\\b" ~ "online",
    pattern == "\\btf\\b" ~ "online",
    pattern == "\\bwtf\\b" ~ "online",
    pattern == "\\blmao\\b" ~ "online",
    pattern == "\\blmfao\\b" ~ "online",
    pattern == "\\brofl\\b" ~ "online",
    pattern == "\\bch[i]*nk[zs]*\\b" ~ "chink",
    pattern == "\\bcoon[zs]*\\b" ~ "coon",
    pattern == "\\b[bull]*crap(ping|ped|s|z|pin)*\\b" ~ "crap",
    pattern == "\\bcum(ming)*\\b" ~ "cum",  
    pattern == "\\bc[o0øöóõ][c¢©]+[(k|<{(|x]+(suck|sak|suk)*[k]*(er|ers|a|az|as)*\\b" ~ "cock",
    pattern == "\\b[kc¢©(][u|µüúû]*nt[zs]*\\b" ~ "cunt",
    pattern == "\\b[d][1!|ïíì][c¢©(][xk|<{(][(head)]*[zs]*\\b" ~ "dick",
    pattern == "\\b[f|=ƒ][a@4äáåe]g[g]*[ioa]*[t]*[zs]*\\b" ~ "fag(got)",

    pattern == "\\bh[o0øöóõ][e3€ëéê][zs]*\\b" ~ "hoe",
    pattern == "\\bh[o0øöóõ]r[e3€ëéê]*[zs]*\\b" ~ "whore",
    pattern == "\\b[k|<{(][i1!ïíìy][k|<{(][e3€ëéê][zs]*\\b" ~ "kike",
    pattern == "\\bn[i1!ïíì]gg[e3€ëéê|@a4äáå][r]*[zs]*\\b" ~ "nigger",
    pattern == "\\bknob[(head)]*[zs]*\\b" ~ "knob",
    pattern == "\\blesbo[sz]*\\b" ~ "lesbo",
    pattern == "\\bming[(a|er)]+(s|z)*\\b" ~ "minger" ,
    pattern == "\\bm[o|u]ron(ic|s|z)*\\b" ~ "moron",
    pattern == "\\bmuff\\b" ~ "muff",
    pattern == "\\bnonce\\b" ~ "nonce",
    pattern == "\\bnympho\\w*\\b" ~ "nympho",
    pattern == "\\bp[e3€ëéê]ck[ae]?[rs]*\\b" ~ "pecker",
    pattern == "\\bp[e3€ëéê]do[philf]*[e]*[zs]*\\b" ~ "pedo",
    pattern == "\\bpik(i|is|ey|ies|eys|eyz|iez|iz)+\\b" ~ "pikey",
    pattern == "\\bpimp(s|ing|in|z|ed)*\\b" ~ "pimp",
    pattern == "\\bp[i1!|ïíì][s5$§z][s5$§]+(in|ing|er|a|ers|erz)*\\b" ~ "piss",
    pattern == "\\bpooft(er|ers|as|az)+\\b" ~ "poofter",
    pattern == "\\bprick[zs]*\\b" ~ "prick",
    pattern == "\\bpuk[e]*(s|z|ing|ed)*\\b" ~ "puke",
    pattern == "\\bp[u|µüúû][s5$§z][s5$§z][@a4äáå]*[y¥][zs]*\\b" ~ "pussy",
    pattern == "\\bqu[e]+[a]*f(s|z|ing|ed)*\\b" ~ "queef",
    pattern == "\\bscr[e]+w(ing|ed|s|z)*\\b" ~ "screw",
    pattern == "\\bshag(ging|gin|ged)*\\b" ~ "shag",
    pattern == "\\bskank[yzs]*\\b" ~ "skank",
    pattern == "\\bslag[zs]*\\b" ~ "slag" ,
    pattern == "\\b[s5$§z]l[uµüúû][t7+†](i|y)*[zs]*\\b" ~ "slut",
    pattern == "\\bsod[d]*[sz]*(ing)*\\b" ~ "sod",
    pattern == "\\bspast(ic|ics|icz)*\\b" ~ "spastic",
    pattern == "\\bretard[zs]*\\b" ~ "retard",
    pattern == "\\btit[t]*(i|ies|ay|ays|ayz)*\\b" ~ "tits",
    pattern == "\\btosser[sz]*\\b" ~ "tosser",
    pattern == "\\btr[a@4äáå]nn(y|ies|iez)+\\b" ~ "tranny",
    pattern == "\\bturd[sz]*\\b" ~ "turd",
    pattern == "\\b[t7+†]w[a@4äáå][t7+†][zs]*\\b" ~ "twat",
    pattern == "\\bw[a@4äáå]n[k|<{(](z|er|ers|ing|az|a|ed)*\\b" ~ "wank",
    pattern == "\\b(cam|man|m)*wh[o0øöóõ]?r[e3€ëéê]*(d|s|z|ing)*\\b" ~ "whore",
    pattern == "\\b[f|=ƒ][-._+ ]*[u|µüúû][-._+ ]*[c¢©(][-._+ ]*[k|<{(][-._+ ]*[s5$§z]*(ing|in|ed)*\\b" ~ "fuck",
    pattern == "\\b[s5$§z][-._+ ]*[h][-._+ ]*[i1!|ïíì]+[-._+ ]*[t7+†][e3€ëéê]*\\b" ~ "shit",
    pattern == "\\b[a@4äáå][-._+ ]*[s5$§z][-._+ ]*[s5$§z]\\b" ~ "ass",
    pattern == "\\b[f=ƒ][c¢©(*k<{(uµüúû*]+(ing|er|a|ed|ers|az)*\\b" ~ "fuck",
    pattern == "\\bf\\b" ~ "fuck",
    pattern == "\\beff(ing|in|ed|d)*\\b" ~ "eff",
T ~ pattern))
# inspect
names(table(kwicdf_annotated$lemma))
```


check kwics

```{r eval = F}
#kwicdf %>%   dplyr::filter(stringr::str_detect(keyword, "\\bjerk")) 
names(table(kwicdf_annotated$keyword))
```

# Clean kwic

```{r}
kwicdf_clean <- kwicdf_annotated %>%
  # Retain rows where 'lemma' is 'hoe' and 'pre' ends with specified phrases
  filter(!(lemma == "hoe" & !str_detect(pre, "(such a( \\w+)?|other|is a|that( \\w+)?)\\b$")))


kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' contains specific unwanted patterns
  filter(!str_detect(keyword, "fak(r|er|ing|ers|ed|e)+")) %>%
  filter(!str_detect(keyword, "fk(r|er|ing|ers|ed|e)+")) %>%
  filter(!str_detect(keyword, "\\w\\+f$")) %>%
  filter(!str_detect(keyword, "n\\|f")) %>%
  filter(!str_detect(keyword, "^\\+f$")) %>%
  filter(!str_detect(keyword, "=(x|a|r|v|c|k|f)")) %>%
  filter(!str_detect(keyword, "(x|a|r|v|c|k|f)=")) %>%
  filter(!str_detect(keyword, "feg(i|o)")) %>%
  filter(!str_detect(keyword, "^feek.*")) %>%
  filter(!str_detect(keyword, "(x|a|r|v|c|k|f)\\+")) %>%
  filter(!str_detect(keyword, "\\+(x|a|r|v|c|k|f)"))  %>%
  dplyr::filter(!str_detect(keyword, "^\\$")) %>%
  dplyr::filter(!str_detect(keyword, "\\d{3}")) %>%
  dplyr::filter(!str_detect(keyword, "\\d{2}=")) %>%
  dplyr::filter(!str_detect(keyword, "fag(a|o)+")) %>%
  dplyr::filter(!str_detect(keyword, "fauk\\w*")) %>%
  dplyr::filter(!str_detect(keyword, "hoess")) %>%
  dplyr::filter(!str_detect(keyword, "z=u")) %>%
  dplyr::filter(!str_detect(keyword, "\\+jug")) %>%
  dplyr::filter(!str_detect(keyword, "2=u")) %>%
  dplyr::filter(!str_detect(keyword, "b=ok")) %>%
  dplyr::filter(!str_detect(keyword, "st=ok")) %>%
  dplyr::filter(!str_detect(keyword, "stat=u")) %>%
  dplyr::filter(!str_detect(keyword, "t=0k")) %>%
  dplyr::filter(!str_detect(keyword, "^feak\\*")) %>%
  dplyr::filter(!str_detect(keyword, "^fc+$")) %>%
  dplyr::filter(!str_detect(keyword, "^f[c]+a.*$")) %>%
  dplyr::filter(!str_detect(keyword, "^fauc.*$")) %>%
  dplyr::filter(!str_detect(keyword, "^f\\$\\d+$"))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'jerk' and 'pre' ends with 'knee' or 'chest'
  filter(!(lemma == "jerk" & str_detect(pre, "(knee|chest)$"))) %>%
  
  # Retain rows where 'lemma' is 'jerk' and:
  # - 'post' starts with 'off', or
  # - 'pre' ends with 'this', 'that', 'such a', or 'is a'
  filter(!(lemma == "jerk" & 
           !(str_detect(post, "^off\\b") | str_detect(pre, "(this|that|such a|is a)\\b$"))))


kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'lemma' is 'eff' and 'post' starts with 'you', 'it', 'off', or 'up'
  filter(!(lemma == "eff" & !str_detect(post, "^(you|it|off|up)"))) 

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'f' unless 'post' starts with specified pronouns or similar words or pre ends with flying
  filter(!(keyword == "f" & !str_detect(post, "^(king|me|you|it|this|that|these|those|him|her|us|them)\\b")| str_detect(pre, "(flying)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'lemma' is 'crap' and 'pre' ends with specified phrases
  filter(!(lemma == "crap" & str_detect(pre, "(metal|poker|roulette)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'lemma' is 'dyke' and 'pre' does not end with specified phrases
  filter(!(lemma == "dyke" & !str_detect(pre, "\\b(a|like|butch|bull|all|fags|as|fucking|club)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'lemma' is 'faggot' and 'pre' ends with specified phrases
  filter(!(keyword == "faggot" & str_detect(post, "(bearer)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'fag' and 'pre'  ends with specified phrases
  filter(!(keyword == "fags" & str_detect(pre, "\\b(of|and|buy|the|few|candy)\\b$") | str_detect(post, "^(to)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'fk' and 'pre' ends with specified phrases
  filter(!(keyword == "fk" & str_detect(pre, "(bryne)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'jiss' and 'pre' ends with specified phrases
  filter(!(keyword == "jizz" & str_detect(pre, "\\b(dns)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'fu' and 'pre' ends with specified phrases
  filter(!(keyword == "fu" & str_detect(pre, "(k(ou)ng)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'knob' and 'post' does not end with specified phrases
  filter(!(lemma == "knob" & !str_detect(post, "^\\b(head[s]?)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'pecker' and 'pre' ends with specified phrases
  filter(!(keyword == "pecker" & str_detect(pre, "\\b(a|wood|of|so)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'lemma' is 'sod' and 'pre' ends with a xxx xxx
  filter(!(lemma == "sod" & !str_detect(pre, "\\ba[n]{0,1}( \\w+)?( \\w+)?$"))) 

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'sodd' and 'post' starts with specified phrases
  filter(!(keyword == "sodd" & str_detect(post, "^\\b(s)\\b")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'sodd' and 'pre' ends with specified phrases
  filter(!(keyword == "sods" & str_detect(pre, "\\band\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Remove rows where 'keyword' is 'tf' and 'pre' does not end with specified phrases
  filter(!(lemma == "tf" & !str_detect(pre, "\\b(how)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # Retain rows where 'keyword' is 'wanka' and 'pre' ends with specified phrases
  filter(!(keyword == "wanka" & !str_detect(pre, "(such a( \\w+)?|other|is a|that( \\w+)?)\\b$")))

kwicdf_clean <- kwicdf_clean %>%
  # remove rows where 'keyword' is 'whor' and 'pre' ends with specified phrases
  filter(!(keyword == "whor" & str_detect(pre, "\\b(casteism)\\b$")))

# inspect
kwicdf_clean[which(kwicdf_clean$keyword == "whrs"),]
#names(table(kwicdf_clean$keyword))
```


Bulk exclusion after manual check

```{r}
exclude <- c("af", "arsel", "arzel", "assle", "asslee", "azzl", "ba$turd", "ba$turd$", "bolivares=u", "chink", "chinks", "chnk", "cnt", "cnts", "coon", "coons", "crap$", "crap=80x", "cum", "daleks=eggs", "darki", "dike", "dikes", "dke", "dkes", "dsh1", "dt=u", "effinded", "eggs=ok", "england=uk", "f$0", "f$1", "f$1$", "f$1$$n$", "f$2", "f$2$", "f$2$$n$", "f$47", "f$50", "f$6", "f$65", "f$78", "f$b", "f$n$", "f$sr", "f$u", "f^a", "f|~n", "f|l", "facke", "faek", "fagg", "faggo", "faggs", "fagi", "fagia", "fagio", "fak", "fanny", "faouk", "fcu", "feack", "feak", "feaked", "feaker", "feaking", "fecke", "feckeed", "feg", "fegg", "fegs", "feka", "feke", "feker", "feock", "feok", "ffs", "fh$f", "fk3", "fka", "fkc", "fkk", "fkkc", "fkkk", "fml", "foak", "fock", "focka", "focke", "focker", "fockers", "foecke", "fok", "foka", "fokaa", "foke", "foker", "food=ok", "fook", "foucker", "fouk", "fouka", "fouke", "frig", "frigg", "fu", "fua", "fuaa", "fuca", "fucc", "fucca", "fuccer", "fued", "fueded", "fueding", "fuek", "fuer", "fuera", "fuerer", "fuing", "fuingers", "fuka", "fuke", "fuku", "fukua", "fuu", "gash", "gok", "goks", "gook", "gone=ok", "gooook", "h=u+pv", "hor", "hore", "hores", "horez", "hors", "horss", "horz", "i=ego", "japss", "japz", "jug", "jugg", "juggs", "juggz", "jugs", "k1kes", "kike", "knobe", "knobes", "knobs", "knobz", "knt", "knts", "kntz", "kunt", "kunts", "kuntz", "l|f", "l21t=u", "lesbos", "lo=uck", "m=uk", "mayai=eggs", "mexico=u", "minga", "mingar", "mingas", "minge", "minger", "mingers", "minges", "muff", "muron", "mwhr", "mwhrs", "n=u", "name=u", "ned=u", "niggars", "nigge", "nigger", "nigges", "nymphoid", "nymphoides", "nympholepsy", "nympholeptic", "nymphomaniacal", "nymphooides", "p=uk", "p1$$d", "peck", "pecka", "pecke", "pecks", "pedoe", "pikey", "piki", "pikies", "pikis", "pissa", "pisser", "pmat=u", "puk", "pukings", "puks", "s=u", "sh1", "sh11", "shag=whoops", "sluty", "smoothie=ek", "soding", "tf", "tit", "titay", "titi", "titt", "titti", "view=uk", "whorings", "whr", "whrd", "whrds", "whre", "whrs", "xian=moron")

kwicdf_clean <- kwicdf_clean %>%
  filter(!keyword %in% exclude)

```


# Remove duplicate rows using dplyr

```{r}
nrow(kwicdf_clean)
kwicdf_clean <- kwicdf_clean %>% dplyr::select(-pattern)
kwicdf_clean <- kwicdf_clean %>% dplyr::distinct()
nrow(kwicdf_clean)
```


check kwics

```{r}
kwicdf_clean[which(kwicdf_clean$keyword == "jizz"),] 
```

# Check KWICs

```{r}
kwicdf_clean %>% filter(corpus == "Malaysia", lemma == "online")
```




# Save KWIC

```{r}
base::saveRDS(kwicdf_clean, file = here::here("test", "kwic_results_clean.rda"))
```


# Outro

```{r}
sessionInfo()
```


