---
title: "Vulgar language on the web across World Englishes - Part 3: data cleaning"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::pdf_document2:
    latex_engine: lualatex
  tufte::tufte_handout:
    latex_engine: xelatex
bibliography: bibliography.bib
link-citations: yes
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Intro

This document shows an analysis that was performed with the aim of finding differences in swearing across geographically distinct varieties of English around the world based on the GloWbe corpus. 

install packages

```{r install, eval = F, message=F, warning=F}
# install packages
install.packages("tidyverse")
install.packages("quanteda")
install.packages("here")
install.packages("udpipe")
install.packages("future")
install.packages("furrr")
install.packages("stringi")
install.packages("parallel")
install.packages("usethis")
install.packages("data.table")
install.packages("ggrepel")
install.packages("writexl")
# devtools::install_github("jimjam-slam/ggflags")
install.packages("ggflags")
```

load packages and set options

```{r act, message=FALSE, warning=FALSE}
# load packages
library(data.table)
library(tidyverse)
library(quanteda)
library(here)
library(stringi)
library(parallel)
library(usethis)
library(data.table)
library(ggflags)
library(ggrepel)
library(writexl)
```

# data cleaning

# loading data

kwics

```{r}
kwics <- base::readRDS(file = here::here("test", "kwic_results_clean.rda")) 
# inspect
head(kwics)
```

differentaite between feck and fuck

```{r}
kwics <- kwics %>%
  dplyr::mutate(lemma = dplyr::case_when(lemma == "fuck" & stringr::str_detect(keyword, "fe[c]*k") ~ "feck",
                                         T ~ lemma))
```


# lemmas retained

number of lemmas

```{r}
length(names(table(kwics$lemma)))
```

lemmas

```{r}
names(table(kwics$lemma))
```


number of forms of lemma fuck

```{r}
kwics %>%
  dplyr::filter(lemma == "fuck") %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(freq = n(), 
                   n = 1) %>%
  dplyr::mutate(n = sum(n))

```

forms of lemma fuck

```{r}
set.seed(20250220)
kwics %>%
  dplyr::filter(lemma == "fuck") %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(freq = n(), 
                   n = 1) %>%
  dplyr::mutate(n = sum(n)) %>% sample_n(20) %>%
  dplyr::pull(keyword) 

```

all forms

```{r}
set.seed(20250220)
kwics %>%
  dplyr::group_by(keyword) %>%
  dplyr::summarise(freq = n(), 
                   n = 1) %>%
  dplyr::mutate(n = sum(n)) %>% 
  dplyr::pull(keyword) 

```


# Checking kwic

```{r}
kwics %>% filter(corpus == "India", lemma == "cum")
```






```{r}
kwicstb <- kwics %>%
  dplyr::mutate(vulgar = 1) %>%
  dplyr::group_by(corpus, docname) %>%
  dplyr::summarise(VulgarTokens = n(),
                   VulgarTypes = length(names(table(keyword))))

# inspect
head(kwicstb)
```



```{r}
glowbetb <- base::readRDS(file = here::here("test", "glowbe_table.rda")) %>%
  dplyr::ungroup()  %>%
  dplyr::mutate(id = 1:nrow(.),
                type = stringr::str_replace_all(file, ".*_([bg])\\d+", "\\1")) %>%
  dplyr::mutate(type = ifelse(type == "g", "General Web", "Blog")) %>%
  dplyr::group_by(corpus) %>%
  dplyr::mutate(docname = paste0("text", 1:length(id)))
# inspect
head(glowbetb)
```


```{r}
glowbetb %>% group_by(corpus, type) %>% summarise(freq = n())
```


test

```{r}
Testtb <- glowbetb %>%
  dplyr::group_by(corpus, type) %>%
  dplyr::summarise(Tokens = sum(tokens))
# inspect
Testtb
```






# combine kwics and glowbe_table

```{r}
res <- dplyr::left_join(glowbetb, kwicstb) %>%
  dplyr::mutate(VulgarTokens = ifelse(is.na(VulgarTokens), 0, VulgarTokens),
                VulgarTypes = ifelse(is.na(VulgarTypes), 0, VulgarTypes))  %>%
  dplyr::mutate(corpus = dplyr::case_when(corpus == "GB-Blog" ~ "Great Britain",
                                          corpus == "GB-General" ~ "Great Britain",
                                          corpus == "US-Blog" ~ "United States",
                                          corpus == "US-General" ~ "United States",
                                          T ~ corpus))
# inspect
head(res, 100); table(res$VulgarTokens)
```




```{r}
res %>%
  group_by(corpus) %>%
  summarise(freq = n(),
            vul = sum(VulgarTokens))
```



# Table 1

```{r}
# Assuming 'res' is your initial data frame
Table1 <- res %>%
  ungroup() %>%
  dplyr::rename(VulgarTexts = VulgarTypes) %>%
  group_by(corpus, type) %>%
  summarise(
    Texts = n(),
     VulgarTexts = sum(ifelse(VulgarTexts > 0, 1, 0), na.rm = TRUE),
    VulgarTokens = sum(VulgarTokens, na.rm = TRUE),
    Tokens = sum(tokens, na.rm = TRUE),
    Percent = round(sum(VulgarTokens, na.rm = TRUE) / sum(tokens, na.rm = TRUE) * 100, 3)
  ) %>%
  rename(
    Region = corpus,
    `Discourse Type` = type
  )

# Calculate totals
totals <- Table1 %>%
  dplyr::ungroup()  %>%
  summarise(
    Region = "Total",
    `Discourse Type` = "",
    Texts = sum(Texts, na.rm = TRUE),
    VulgarTexts = sum(VulgarTexts, na.rm = TRUE),
    VulgarTokens = sum(VulgarTokens, na.rm = TRUE),
    Tokens = sum(Tokens, na.rm = TRUE),
    Percent = round(sum(VulgarTokens, na.rm = TRUE) / sum(Tokens, na.rm = TRUE) * 100, 3)
  )

# Bind the totals row to the original summary
Table1 <- bind_rows(Table1, totals)

# save 
writexl::write_xlsx(Table1, here::here("tables", "Table1.xlsx"))
# inspect
Table1
```


# Figure 1

```{r}
res  %>%
    ungroup() %>%
  dplyr::rename(VulgarTexts = VulgarTypes) %>%
  dplyr::group_by(corpus) %>%
  dplyr::summarise(Texts = n(),
                   VulgarTexts = sum(ifelse(VulgarTexts > 0, 1, 0), na.rm = TRUE),,
                   VulgarTokens = sum(VulgarTokens),
                   Tokens = sum(tokens)) %>%
  dplyr::mutate(Percent =  round(VulgarTokens/Tokens *100, 3)) %>%
  dplyr::mutate(Kachru = dplyr::case_when(corpus == "Australia" ~ "Inner circle",
                                          corpus == "Canada" ~ "Inner circle",
                                          corpus == "Great Britain" ~ "Inner circle",
                                          corpus == "Ireland" ~ "Inner circle",
                                          corpus == "New Zealand" ~ "Inner circle",
                                          corpus == "United States" ~ "Inner circle",
                                          T ~ "outer circle")) %>%
  dplyr::mutate(country = dplyr::case_when(corpus == "Australia" ~ "au",
                                           corpus == "Bangladesh" ~ "bd",
                                           corpus == "Canada" ~ "ca",
                                           corpus == "Great Britain" ~ "gb",
                                           corpus == "Ghana" ~ "gh",
                                           corpus == "Hong Kong" ~ "hk",
                                          corpus == "Ireland" ~ "ie",
                                          corpus == "India" ~ "in",
                                          corpus == "Jamaica" ~ "jm",
                                          corpus == "Kenya" ~ "ke",
                                          corpus == "Malaysia" ~ "my",
                                          corpus == "New Zealand" ~ "nz",
                                          corpus == "Nigeria" ~ "ng",
                                          corpus == "Pakistan" ~ "pk",
                                          corpus == "Philippines" ~ "ph",
                                          corpus == "Singapore" ~ "sg",
                                          corpus == "South Africa" ~ "za",
                                          corpus == "Sri Lanka" ~ "lk",
                                          corpus == "Tanzania" ~ "tz",
                                          corpus == "United States" ~ "us",
                                          T ~ NA)) -> Figure1dat
# inspect
head(Figure1dat)
```



```{r}
Figure1dat %>%
  ggplot(aes(x = reorder(corpus, Percent), 
             y = Percent, 
             country = country, 
             label = Percent, 
             fill = Kachru)) +
  geom_bar(stat = "identity") +
  ggflags::geom_flag(size = 4) +
   geom_text(hjust = -1.1, color = "black", size = 3)+
  coord_flip(ylim = c(0, 0.05)) +
  scale_fill_manual(values = c("gray90", "gray70")) +
  theme_bw() +
  labs(xlab = "", ylab = "Percent") +
  theme(legend.position = c(0.8, 0.5),
        legend.title = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y=element_blank())
ggsave(here::here("images", "Fig1.png"), width = 14, height = 10, units = "cm", dpi = 600)
```


# Figure 2

```{r}
res  %>%
  ungroup() %>%
  dplyr::rename(VulgarTexts = VulgarTypes) %>%
  dplyr::group_by(corpus, type) %>%
    dplyr::summarise(Texts = n(),
                   VulgarTexts = sum(ifelse(VulgarTexts > 0, 1, 0), na.rm = TRUE),,
                   VulgarTokens = sum(VulgarTokens),
                   Tokens = sum(tokens)) %>%
  dplyr::mutate(Percent =  round(VulgarTokens/Tokens *100, 3)) %>%
  dplyr::mutate(Kachru = dplyr::case_when(corpus == "Australia" ~ "Inner circle",
                                          corpus == "Canada" ~ "Inner circle",
                                          corpus == "Great Britain" ~ "Inner circle",
                                          corpus == "Ireland" ~ "Inner circle",
                                          corpus == "New Zealand" ~ "Inner circle",
                                          corpus == "United States" ~ "Inner circle",
                                          T ~ "outer circle")) %>%
  dplyr::mutate(country = dplyr::case_when(corpus == "Australia" ~ "au",
                                           corpus == "Bangladesh" ~ "bd",
                                           corpus == "Canada" ~ "ca",
                                           corpus == "Great Britain" ~ "gb",
                                           corpus == "Ghana" ~ "gh",
                                           corpus == "Hong Kong" ~ "hk",
                                          corpus == "Ireland" ~ "ie",
                                          corpus == "India" ~ "in",
                                          corpus == "Jamaica" ~ "jm",
                                          corpus == "Kenya" ~ "ke",
                                          corpus == "Malaysia" ~ "my",
                                          corpus == "New Zealand" ~ "nz",
                                          corpus == "Nigeria" ~ "ng",
                                          corpus == "Pakistan" ~ "pk",
                                          corpus == "Philippines" ~ "ph",
                                          corpus == "Singapore" ~ "sg",
                                          corpus == "South Africa" ~ "za",
                                          corpus == "Sri Lanka" ~ "lk",
                                          corpus == "Tanzania" ~ "tz",
                                          corpus == "United States" ~ "us",
                                          T ~ NA))  -> Figure2dat
# inspect
head(Figure2dat)
```



```{r}
Figure2dat %>%
  ggplot(aes(x = reorder(corpus, Percent), 
             y = Percent, 
             country = country, 
             label = Percent, 
             fill = type)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  ggflags::geom_flag(aes(y = 0), size = 4) +
  geom_text(color = "black", hjust = -0.2, size = 3, position = position_dodge(width = .9))+
  coord_flip(ylim = c(0, 0.05)) +
  scale_fill_manual(breaks = c("General Web", "Blog"), values = c("gray90", "gray70")) +
  theme_bw() +
  labs(xlab = "", ylab = "Percent") +
  theme(legend.position = c(0.7, 0.3),
        legend.title = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y=element_blank())
ggsave(here::here("images", "Fig2.png"), width = 14, height = 14, units = "cm", dpi = 600)
```

# Figure 3

```{r}
Table1  %>%
  dplyr::mutate(PercentVulgar =  round((VulgarTexts/Texts) *100, 1)) %>%
  dplyr::filter(Region != "Total") %>%
  dplyr::mutate(Kachru = dplyr::case_when(Region == "Australia" ~ "Inner circle",
                                          Region == "Canada" ~ "Inner circle",
                                          Region == "Great Britain" ~ "Inner circle",
                                          Region == "Ireland" ~ "Inner circle",
                                          Region == "New Zealand" ~ "Inner circle",
                                          Region == "United States" ~ "Inner circle",
                                          T ~ "outer circle")) %>%
  dplyr::mutate(country = dplyr::case_when(Region == "Australia" ~ "au",
                                           Region == "Bangladesh" ~ "bd",
                                           Region == "Canada" ~ "ca",
                                           Region == "Great Britain" ~ "gb",
                                           Region == "Ghana" ~ "gh",
                                           Region == "Hong Kong" ~ "hk",
                                          Region == "Ireland" ~ "ie",
                                          Region == "India" ~ "in",
                                          Region == "Jamaica" ~ "jm",
                                          Region == "Kenya" ~ "ke",
                                          Region == "Malaysia" ~ "my",
                                          Region == "New Zealand" ~ "nz",
                                          Region == "Nigeria" ~ "ng",
                                          Region == "Pakistan" ~ "pk",
                                          Region == "Philippines" ~ "ph",
                                          Region == "Singapore" ~ "sg",
                                          Region == "South Africa" ~ "za",
                                          Region == "Sri Lanka" ~ "lk",
                                          Region == "Tanzania" ~ "tz",
                                          Region == "United States" ~ "us",
                                          T ~ NA))   -> Fig3dat
# inspect
Fig3dat
```


```{r}
Fig3dat %>%
  ggplot(aes(x = reorder(Region, PercentVulgar), 
             y = PercentVulgar, 
             country = country, 
             label = PercentVulgar, 
             fill = `Discourse Type`)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  ggflags::geom_flag(aes(y = 0), size = 4) +
  geom_text(color = "black", hjust = -0.5, size = 3, position = position_dodge(width = .9))+
  coord_flip(ylim = c(0, 15)) +
  scale_fill_manual(breaks = c("General Web", "Blog"), values = c("gray90", "gray70")) +
  theme_bw() +
  theme(legend.position = c(0.7, 0.3),
        legend.title = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y=element_blank()) +
  labs(xlab = "", ylab = "Percent") 
ggsave(here::here("images", "Fig3.png"), width = 14, height = 14, units = "cm", dpi = 600)
```

# Figure 4 (CTTR)

```{r}
#head(kwics)
kwics   %>%
  dplyr::mutate(corpus = dplyr::case_when(corpus == "GB-Blog" ~ "Great Britain",
                                          corpus == "GB-General" ~ "Great Britain",
                                          corpus == "US-Blog" ~ "United States",
                                          corpus == "US-General" ~ "United States",
                                          T ~ corpus)) %>%
  dplyr::group_by(corpus) %>%
  dplyr::summarise(tokens = length(names(table(keyword))),
                   types = length(names(table(lemma)))) %>%
  dplyr::mutate(CTTR = round(types / (sqrt(2 * tokens)), 3)) %>%
  dplyr::mutate(country = dplyr::case_when(corpus == "Australia" ~ "au",
                                           corpus == "Bangladesh" ~ "bd",
                                           corpus == "Canada" ~ "ca",
                                           corpus == "Great Britain" ~ "gb",
                                           corpus == "Ghana" ~ "gh",
                                           corpus == "Hong Kong" ~ "hk",
                                          corpus == "Ireland" ~ "ie",
                                          corpus == "India" ~ "in",
                                          corpus == "Jamaica" ~ "jm",
                                          corpus == "Kenya" ~ "ke",
                                          corpus == "Malaysia" ~ "my",
                                          corpus == "New Zealand" ~ "nz",
                                          corpus == "Nigeria" ~ "ng",
                                          corpus == "Pakistan" ~ "pk",
                                          corpus == "Philippines" ~ "ph",
                                          corpus == "Singapore" ~ "sg",
                                          corpus == "South Africa" ~ "za",
                                          corpus == "Sri Lanka" ~ "lk",
                                          corpus == "Tanzania" ~ "tz",
                                          corpus == "United States" ~ "us",
                                          T ~ NA))  -> Fig4dat
Fig4dat
```


```{r}
ggplot(Fig4dat, aes(x = CTTR, y = reorder(corpus, -CTTR), country = country, label = CTTR)) +
  geom_text(color = "black", hjust = -0.5, size = 3, position = position_dodge(width = .9))+
  ggflags::geom_flag(size = 4) +
  theme_bw() +
  coord_cartesian(xlim = c(2, 4)) +
  theme(legend.position = c(0.7, 0.3),
        legend.title = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.title.y=element_blank()) +
  labs(x = "Adjusted Corrected Type-Token Ratio (aCTTR)")
ggsave(here::here("images", "Fig4.png"), width = 16, height = 12, units = "cm", dpi = 600)
```




# Figure 5 (lemmas)

```{r}
kwics  %>%
  dplyr::mutate(corpus = dplyr::case_when(corpus == "GB-Blog" ~ "Great Britain",
                                          corpus == "GB-General" ~ "Great Britain",
                                          corpus == "US-Blog" ~ "United States",
                                          corpus == "US-General" ~ "United States",
                                          T ~ corpus)) %>%
  group_by(corpus, lemma) %>%
  dplyr::summarise(freq = n()) -> Fig5dat_1
# inspect
Fig5dat_1
```


```{r}
res %>%
  dplyr::group_by(corpus) %>%
  dplyr::summarise(tokens = sum(tokens)) -> Fig5dat_2
# inspect
Fig5dat_2
```


```{r}
dplyr::left_join(Fig5dat_2, Fig5dat_1) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(rfreq = freq/tokens*1000000)  %>%
  dplyr::mutate(lemma = ifelse(rfreq < 10, "other", lemma)) %>%
  dplyr::group_by(corpus, lemma) %>%
  dplyr::summarise(tokens = unique(tokens),
                   freq = sum(freq))  %>%
  dplyr::mutate(rfreq = freq/tokens*1000000) %>%
  dplyr::group_by(corpus) %>%
  dplyr::mutate(maxfreq = max(rfreq))  %>%
  dplyr::mutate(country = dplyr::case_when(corpus == "Australia" ~ "au",
                                           corpus == "Bangladesh" ~ "bd",
                                           corpus == "Canada" ~ "ca",
                                           corpus == "Great Britain" ~ "gb",
                                           corpus == "Ghana" ~ "gh",
                                           corpus == "Hong Kong" ~ "hk",
                                          corpus == "Ireland" ~ "ie",
                                          corpus == "India" ~ "in",
                                          corpus == "Jamaica" ~ "jm",
                                          corpus == "Kenya" ~ "ke",
                                          corpus == "Malaysia" ~ "my",
                                          corpus == "New Zealand" ~ "nz",
                                          corpus == "Nigeria" ~ "ng",
                                          corpus == "Pakistan" ~ "pk",
                                          corpus == "Philippines" ~ "ph",
                                          corpus == "Singapore" ~ "sg",
                                          corpus == "South Africa" ~ "za",
                                          corpus == "Sri Lanka" ~ "lk",
                                          corpus == "Tanzania" ~ "tz",
                                          corpus == "United States" ~ "us",
                                          T ~ NA))  -> Fig5dat
# inspect
Fig5dat
```

```{r}
Fig5dat %>%
  ggplot(aes(x = reorder(corpus, maxfreq), y = rfreq, group = lemma, label = lemma, country = country, alpha = lemma)) +
  geom_text(size = 3, position=position_jitter(width=.3,height=.3)) +
  ggflags::geom_flag(aes(y = -10), size = 4) +
  coord_flip() +
  labs(x = "", 
       y = "Relative frequency (per million words)",
       alpha = "Vulgar lemma") +
  #scale_alpha_manual(values = rep(.5, length(names(table(Fig5dat$lemma))))) +
  scale_alpha_manual(values = c(0.5, 0.5, 0.5, 0.5, 0.5, 0.9,  0.5, 0.5, 0.5,  0.9, 0.5, 0.5)) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "top")
ggsave(here::here("images", "Fig5.png"), width = 15, height = 20, units = "cm", dpi = 600)
  
```

# Figure 6 (heatmap)

```{r}
kwics %>%
  dplyr::mutate(corpus = dplyr::case_when(corpus == "GB-Blog" ~ "Great Britain",
                                          corpus == "GB-General" ~ "Great Britain",
                                          corpus == "US-Blog" ~ "United States",
                                          corpus == "US-General" ~ "United States",
                                          T ~ corpus)) %>%
  dplyr::group_by(corpus, lemma) %>%
  dplyr::summarise(freq = n(), .groups = "drop") %>%
  mutate(z_score = scale(freq)) -> cfadat
# inspect
head(cfadat)
```

## CFA

```{r}
library(cfa)
# define configurations
configs <- cfadat %>%
  dplyr::select(corpus, lemma)
# define counts
counts <- cfadat$freq
# perform cfa
cfa(configs, counts) -> cfa_res
# inspect
cfa_res
```

```{r}
options(scipen=999)
cfa_res[[1]] %>%
  as.data.frame()  %>%
  dplyr::filter(sig.chisq == "TRUE")  -> cfares
```


```{r}
cfa_res[[1]] %>%
  as.data.frame() %>%
  dplyr::mutate(lemma = stringr::str_remove_all(label, ".* "),
                corpus = stringr::str_replace_all(label, "^(\\w+ {0,1}\\w*) \\w+.*$", "\\1")) %>%
  dplyr::group_by(corpus) %>%
  dplyr::mutate(corpus_total = sum(n)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(lemma) %>%
  dplyr::mutate(lemma_total = sum(n)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(total = sum(n)) %>%
  dplyr::rowwise() %>%
  dplyr::mutate(phi = (sqrt(chisq / total)))  %>%
  dplyr::mutate(phi = ifelse(n > expected, phi, -phi)) %>%
  dplyr::mutate(phi = ifelse(is.na(phi), 0, phi))  %>%
  mutate(phi = ifelse(phi < -0.02 | phi > 0.02, phi, 0),
         phi = ifelse(is.na(phi), 0, phi)) %>%
  dplyr::mutate(corpus = factor(corpus, levels = c("United States", "Great Britain", "Australia", "Canada", "Ireland", "New Zealand", "India", "Nigeria", "Philippines", "Pakistan", "Singapore", "South Africa", "Ghana", "Kenya", "Malaysia", "Hong Kong", "Jamaica", "Tanzania", "Sri Lanka", "Bangladesh"))) -> Fig6dat
# inspect
Fig6dat
```



```{r}
# Create heatmap
ggplot(Fig6dat, aes(x = corpus, y = lemma, fill = phi)) +
  geom_tile() +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  theme_minimal() +
  labs(
    title = "",
    x = "Region",
    y = "Vulgar Lemma",
    fill = "Phi-value"
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
    panel.background = element_rect(fill = "white", color = NA), # Set panel background to white
    plot.background = element_rect(fill = "white", color = NA),
    panel.grid = element_blank())   # Set plot background to white
ggsave(here::here("images", "Fig6.png"), width = 15, height = 22, units = "cm", dpi = 600,bg = "white")
```

## Table 2

```{r}
Table2 <- Fig6dat %>%
  dplyr::filter(sig.chisq == T) %>%
  dplyr::select(-label, -z, -p.z, -sig.z, -corpus_total, -lemma_total, -total, -sig.chisq) %>%
  dplyr::mutate(type = ifelse(phi < 0, "Avoided", "Preferred"),
                p.chisq = ifelse(p.chisq < 0.001, "< .001***", p.chisq),
                Q = round(Q, 5),
                expected = round(expected, 1),
                chisq = round(chisq, 1),
                phi = round(phi, 3)) %>%
  dplyr::arrange(-phi) %>%
  dplyr::relocate(any_of(c("corpus", "lemma", "type", "n", "expected", "chisq", "Q"))) %>%
  dplyr::rename(Region = corpus,
                `Vulgar lemma` = lemma,
                `Observed frequency` = n,
                `Expected frequency` = expected,
                `Q-value`	= Q,
                `X2-value` = chisq,
                `Bonferroni-corrected p-value` = p.chisq,
                Type = type,
                `Phi-value` = phi)
# save 
writexl::write_xlsx(Table2, here::here("tables", "Table2.xlsx"))
# inspect
Table2
```

# Outro

```{r}
sessionInfo()
```

